\newenvironment{projectlong}[2]{%
  \begin{tabularx}{\linewidth}{@{}X r@{}}
    \textbf{#1} & #2 \\[3pt]
  \end{tabularx}
  \begin{minipage}[t]{0.85\linewidth} % adjust width (e.g., 0.85–0.9)
  \begin{itemize}[leftmargin=1em, label=--, topsep=2pt, itemsep=3pt]
}{%
  \end{itemize}
  \end{minipage}
  \vspace{0.6em} % <-- add or adjust this (e.g., 0.5em–1em)
}



\section*{Projects}

\begin{projectlong}{A Foundation Model for EEG}{2024--Present}
    \item Developing a novel large-scale hybrid foundation model for EEG that unifies temporal, spatial, and spectral representations of neural activity.
    \item Designed to generalize across datasets, channel configurations, and temporal resolutions.
    \item Builds upon prior work with transformer and state-space architectures to model long-range neural dependencies.
\end{projectlong}


\begin{projectlong}{Uncovering the Role of the Thalamus in Epilepsy}{2023--Present}
    \item Investigating thalamocortical network dynamics in pediatric epilepsy through SEEG and functional connectivity analysis.
    \item Developing deep learning models to inform closed-loop stimulation strategies for seizure prevention.
\end{projectlong}


\begin{projectlong}{Identifying the Neural Correlates of Gait}{2024--Present}
    \item Analyzing joint EEG and gait data to uncover neural mechanisms underlying locomotion.
    \item Investigating factors that determine patient response to non-invasive gait interventions.
    \item Developing contrastive learning methods to align noisy EEG and gait representations.
\end{projectlong}
